Manifold Destiny - or how to rig an election

### 2024-07-07 index.qmd
metda

# Testing
## Installling packages
```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
```

@@

```{webr-r}
ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
ad
```

>>>>

# Testing
## ABC
Write some text here
```{web-r}
```

abc

## Installling packages
```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
# readr::read.csv("/tmp/RtmpHKcMHo/d5ace5deaed228c73ccaf4fb/0.csv")
```

@@

```{webr-r}
# ad <- readr::read_csv("https://raw.githubusercontent.com/lotariohw26/ManifoldDestiny/main/data-raw/csv/full_apps_data.csv")
# ad
```
